---
title: "Squirrel Data"
author: "Pia Cadar"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import data set
```{r Import Data}
# Read dataset
library(car)
squirrel = read.csv('squirrel.csv')
squirrel
```

Split data into different categories for analysis
```{r Split Data}
# Split data into categories
food <- squirrel[squirrel$Food == 'Yes',]
no_food <- squirrel[squirrel$Food == 'No',]
low_density <- squirrel[squirrel$Density == 'Low',]
low_density_food <- low_density[low_density$Food == 'Yes',]
low_density_no_food <- low_density[low_density$Food == 'No',]
high_density <- squirrel[squirrel$Density == 'High',]
high_density_food <- high_density[high_density$Food == 'Yes',]
high_density_no_food <- high_density[high_density$Food == 'No',]

```

Experiment 1: High Density with food vs. Low Density with food
Boxplot was created and a Welch Two Sample T-test was conducted
```{r Experiment 1: Boxplot}
# Create boxplot
boxplot(food$Tail.Flicks~food$Density,
        main = "Tail Flick vs. Density in the presence of food",
        xlab = "Density",
        ylab = "Tail Flicks",
        col = c("light blue", "orange"),
)
```
```{r Experiment 1: Levene's Test}
# Conduct Levene's test to check assumptions
leveneTest(food$Tail.Flicks~food$Density)
```
```{r Experiment 1: T-test}
# Conduct Welch Two Sample T-test
t.test(food$Tail.Flicks~food$Density, paired = F, var.equal=F)
```

Experiment 2: High Density without food vs. Low Density without food
Boxplot was created and a Wilcox was conducted
```{r Experiment 2: Boxplot}
# Create boxplot
boxplot(no_food$Tail.Flicks~no_food$Density,
        main = "Tail Flick vs. Density without the presence of food",
        xlab = "Density",
        ylab = "Tail Flicks",
        col = c("light blue", "orange"),
)
```
```{r Experiment 2: Levene's Test}
# Conduct Levene's test to check assumptions
leveneTest(Tail.Flicks~Density, data = no_food)
```
Assumptions from Levene's test were not met, Wilcox test run instead
```{r Experiment 2: T-test}
# Conduct Wilcox Two Sample T-test
wilcox.test(Tail.Flicks~Density, data = no_food)
```

Experiment 3: Low Density with food vs. Low Density without food
Boxplot was created and a Wilcox test was conducted
```{r Experiment 3: Boxplot}
# Create boxplot
boxplot(low_density$Tail.Flicks~low_density$Food,
        main = "Tail Flick vs. Food in low density areas",
        xlab = "Food Present",
        ylab = "Tail Flicks",
        col = c("light blue", "orange"),
)
```
```{r Experiment 3: Levene's Test}
# Conduct Levene's test to check assumptions
leveneTest(Tail.Flicks~Food, data = low_density)
```
```{r Experiment 3: T-test}
# Conduct Wilcox Two Sample T-test
wilcox.test(Tail.Flicks~Food, data = low_density)
```

Experiment 4: High Density with food vs. High Density without food
Boxplot was created and a Wilcox test was conducted
```{r Experiment 4: Boxplot}
# Create boxplot
boxplot(high_density$Tail.Flicks~high_density$Food,
        main = "Tail Flick vs. Food in high density areas",
        xlab = "Food Present",
        ylab = "Tail Flicks",
        col = c("light blue", "orange"),
)
```
```{r Experiment 4: Levene's Test}
# Conduct Levene's test to check assumptions
leveneTest(Tail.Flicks~Food, data = high_density)
```
```{r Experiment 4: T-test}
# Conduct Wilcox Two Sample T-test
wilcox.test(Tail.Flicks~Food, data = high_density)
```
